Constructing Sailing Match Race Schedules: Round-Robin Pairing Lists

### 2015-04-13 paper.tex
Fix rule numbering

\begin{framed}
\noindent Principal Criteria in Order of Priority:
\begin{enumerate}
\item Each skipper sails against each other skipper once.
\item[2*.] When skippers have an even number of matches, they have the same number of port and starboard
    assignments.
\item[3*.] When skippers have an odd number of matches, the first half of the skippers will have one
    more starboard assignment.
\item No skipper in the last match of a flight should be in the first match of the next flight.
\item No skipper should have more than two consecutive port or starboard assignments.
\item Each skipper should be assigned to match 1, match 2, etc. in a flight as equally as possible.
\item In flights with five or more matches, no skipper should be in the next-to-last match in a
    flight and then in the first match of the next flight.
\item If possible, a skipper should be starboard when meeting the nearest lowest ranked skipper
    (i.e.\ \#1 will be starboard against \#2, \#3 will be starboard against \#4).
\item Close-ranked skippers meet in the last flight.
\item Minimise the number of boat changes.
\item Skippers in the last match of a flight do not change boats.
\item Skippers in new boats do not sail in the first match of the next flight.
\item Skippers have a reasonable sequence of matches and blanks.
\end{enumerate}
Note that criteria~10, 11 and~12 only apply when there are fewer boats than skippers; 11 and~12
override~6 when changes are required, and~13 applies when there are more boats than skippers.
\end{framed}

>>>>

\begin{framed}
\noindent Principal Criteria in Order of Priority:
\begin{enumerate}
\item[1.] Each skipper sails against each other skipper once.
\item[2*.] When skippers have an even number of matches, they have the same number of port and starboard
    assignments.
\item[3*.] When skippers have an odd number of matches, the first half of the skippers will have one
    more starboard assignment.
\item[4.] No skipper in the last match of a flight should be in the first match of the next flight.
\item[5.] No skipper should have more than two consecutive port or starboard assignments.
\item[6.] Each skipper should be assigned to match 1, match 2, etc. in a flight as equally as possible.
\item[7.] In flights with five or more matches, no skipper should be in the next-to-last match in a
    flight and then in the first match of the next flight.
\item[8.] If possible, a skipper should be starboard when meeting the nearest lowest ranked skipper
    (i.e.\ \#1 will be starboard against \#2, \#3 will be starboard against \#4).
\item[9.] Close-ranked skippers meet in the last flight.
\item[10.] Minimise the number of boat changes.
\item[11.] Skippers in the last match of a flight do not change boats.
\item[12.] Skippers in new boats do not sail in the first match of the next flight.
\item[13.] Skippers have a reasonable sequence of matches and blanks.
\end{enumerate}
Note that criteria~10, 11 and~12 only apply when there are fewer boats than skippers; 11 and~12
override~6 when changes are required, and~13 applies when there are more boats than skippers.
\end{framed}
